Distinguishing among coalescent models using two-site allele frequency spectra

### 2018-08-16 manuscript/manuscript.tex
Rename some figures.
Rename more figures.

\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{figures/wfpmi_growth_beta.pdf}
\caption{Weighted frequency pointwise mutual information for three coalescent models: the time-homogeneous Kingman coalescent, the Kingman coalescent with exponential growth ($g=4$), and the beta coalescent ($\alpha=1.45$). For all models $n=39$. Growth and $\alpha$ parameters were chosen to generate average SFS with similar Tajima's D. The diagonal $i=j$ is masked. \label{fig:nonrecombining_pmi}}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=0.8\textwidth]{figures/figure2.pdf}
\caption{Pointwise mutual information between singletons and non-singletons for Kingman coalescents with exponential growth and beta coalescents. The exponential growth rate, $g$, ranges from 0.25 to 8.0 in coalescent time units. The beta coalescent parameter, $\alpha$, ranges from 1.75 (nearly Kingman) to 1.25 (nearly Bolthausen-Sznitman). \label{fig:fpmi_vs_tajimasd}}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=0.8\textwidth]{figures/figure4.pdf}
\caption{Weighted frequency pointwise information for three recombination rates with sample size $n=100$. As in \Fig{fig:nonrecombining_pmi}, the diagonal elements are masked, and the growth and multiple-merger parameters were chosen to generate average SFS with similar Tajima's D. \label{fig:wpmi_recombination}}
\end{figure}

\Fig{fig:wpmi_recombination} shows the weighted $\fpmi$ for three genetic distances in a constant-$N$ Kingman coalescent, a Kingman coalescent with exponential growth, and a beta coalescent.
As in the non-recombining case, the constant-$N$ and exponential-growth Kingman models have similar $\fpmi$.
In both models, $\fpmi > 0$ for $i\approx j$ for $r\E{T_2} \sim 1$.
This is presumably because trees at nearby sites contain clades with similar numbers of leaves.
These positive correlations do not extend to $i \gg j$, which is the signal of multiple mergers in our binned $\hilopmi$.
On the other hand, the positive $\fpmi$ in the beta coalescent persists for $r\E{T_2} > 1$.
Thus, the signal of multiple mergers in $\fpmi$ is robust to recombination.

@@

\begin{figure}
\centering
\includegraphics[width=0.8\textwidth]{figures/figure3.pdf}
\caption{Distortions in $\fpmi$ vs. distortions in the SFS for $n=4$. Parameters for beta coalescents and exponential growth are as in \fig{fig:fpmi_vs_tajimasd}. For the piecewise-constant--$N$ model, the fold-change in $N$ varies from 2 to $2^4$ and the time of this change varies from $2^{-4}$ to 2 in coalescent time units. \label{fig:sdpmi_vs_sdratio}}
\end{figure}

>>>>

\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{figures/wfpmi_no_recombination.pdf}
\caption{Weighted frequency pointwise mutual information for three coalescent models: the time-homogeneous Kingman coalescent, the Kingman coalescent with exponential growth ($g=4$), and the beta coalescent ($\alpha=1.45$). For all models $n=39$. Growth and $\alpha$ parameters were chosen to generate average SFS with similar Tajima's D. The diagonal $i=j$ is masked. \label{fig:nonrecombining_pmi}}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=0.8\textwidth]{figures/hilopmi_vs_tajimasD.pdf}
\caption{Pointwise mutual information between singletons and non-singletons for Kingman coalescents with exponential growth and beta coalescents. The exponential growth rate, $g$, ranges from 0.25 to 8.0 in coalescent time units. The beta coalescent parameter, $\alpha$, ranges from 1.75 (nearly Kingman) to 1.25 (nearly Bolthausen-Sznitman). \label{fig:fpmi_vs_tajimasd}}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=0.8\textwidth]{figures/wfpmi_with_recombination.pdf}
\caption{Weighted frequency pointwise information for three recombination rates with sample size $n=100$. As in \Fig{fig:nonrecombining_pmi}, the diagonal elements are masked, and the growth and multiple-merger parameters were chosen to generate average SFS with similar Tajima's D. \label{fig:wfpmi_recombination}}
\end{figure}

\Fig{fig:wfpmi_recombination} shows the weighted $\fpmi$ for three genetic distances in a constant-$N$ Kingman coalescent, a Kingman coalescent with exponential growth, and a beta coalescent.
As in the non-recombining case, the constant-$N$ and exponential-growth Kingman models have similar $\fpmi$.
In both models, $\fpmi > 0$ for $i\approx j$ for $r\E{T_2} \sim 1$.
This is presumably because trees at nearby sites contain clades with similar numbers of leaves.
These positive correlations do not extend to $i \gg j$, which is the signal of multiple mergers in our binned $\hilopmi$.
On the other hand, the positive $\fpmi$ in the beta coalescent persists for $r\E{T_2} > 1$.
Thus, the signal of multiple mergers in $\fpmi$ is robust to recombination.

@@

\begin{figure}
\centering
\includegraphics[width=0.8\textwidth]{figures/singleton-doubleton.pdf}
\caption{Distortions in $\fpmi$ vs. distortions in the SFS for $n=4$. Parameters for beta coalescents and exponential growth are as in \fig{fig:fpmi_vs_tajimasd}. For the piecewise-constant--$N$ model, the fold-change in $N$ varies from 2 to $2^4$ and the time of this change varies from $2^{-4}$ to 2 in coalescent time units. \label{fig:sdpmi_vs_sdratio}}
\end{figure}
